---
title: "Cabbages"
author: "Precious Calderon"
date: "Summer 2022"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(MASS)
veggy <- cabbages
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
 The cabbages data from the MASS package is loaded into a dataframe called veggy. Complete this report by answering the following two questions  
 
### Is there a difference in average VitC between c39 and c52 cultivation methods?  

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
boxplot(VitC~Cult,data=veggy)
```
  
The median value for the VitC content in cabbages cultivated using the c39 method is shown to be at about 50 units while the median value for the VitC content in cabbages cultivated using the c52 method is around 65 units. Overall, cabbages cultivated using the c52 method generally contain more VitC as shows by the box plot range that is higher than the range of the other method.  
  
### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
favstats(VitC~Cult,data=veggy)
```
  
The average VitC content of cabbages cultivated using the c39 method is 51.5 units while the average VitC content of cabbages cultivated using the c52 method is 64.4 units.   
  
## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
t.test(VitC~Cult,data=veggy)
```
  
The t-test shows, similar to the numerical descriptive results, that the average VitC content of cabbages cultivated using the c39 method is 51.5 units while it is 64.4 units for cabbages for cabbages cultivated using the c52 method. Moreover, the p-value which is a very low value shows that there is a very small probability the there is no difference between the VitC content of cabbages using the two cultivation methods being discussed.   
  
# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
  
Given that the graphical descriptive, numerical descriptive, and inferential results all show that there is a difference between the VitC content of cabbages produced using the c39 and the c52 cultivating methods, we can conclude that the c39 and c52 cultivation methods produce cabbages with different VitC content.   